Red-Giant Hot Jupiters: Brilliant Radio Beacons? \memoTM{Since they are not that bright, maybe ``The Radio Emission from Red-Giant Hot Jupiters'' or ``A Novel Method for Detecting Red-Giant Hot Jupiters'' would be a better title?}

### 2015-09-09 ms.tex
Added Stitch Fix affiliation.

\author{
%
Yuka Fujii\altaffilmark{1} 
%
David S. Spiegel\altaffilmark{2,3}
%
Tony Mroczkowski\altaffilmark{4,5}
%
Jason Nordhaus\altaffilmark{6,7}\\
%
Neil T. Zimmerman\altaffilmark{8}
%
Aaron Parsons\altaffilmark{9}
%
Nikku Madhusudhan\altaffilmark{10}
%
Mehrdad Mirbabayi\altaffilmark{2}
}

@@

\affil{$^4$National Research Council Fellow}

\affil{$^5$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}

\affil{$^6$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^7$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^8$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}

\affil{$^9$Astronomy Department, University of California Berkeley}

\affil{$^{10}$Astronomy Department, University of Cambridge, UK}

>>>>

\author{
%
Yuka Fujii\altaffilmark{1} 
%
David S. Spiegel\altaffilmark{2,3,4}
%
Tony Mroczkowski\altaffilmark{5,6}
%
Jason Nordhaus\altaffilmark{7,8}\\
%
Neil T. Zimmerman\altaffilmark{9}
%
Aaron Parsons\altaffilmark{10}
%
Nikku Madhusudhan\altaffilmark{11}
%
Mehrdad Mirbabayi\altaffilmark{13}
}

@@

\affil{$^4$Analytics \& Algorithms, Stitch Fix,
  San Francisco, CA  94103}

\affil{$^5$National Research Council Fellow}

\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}

\affil{$^7$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^8$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^9$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}

\affil{$^{10}$Astronomy Department, University of California Berkeley}

\affil{$^{11}$Astronomy Department, University of Cambridge, UK}
